Preliminary Thesis Defence

### 2014-01-05 south-africa.tex
update results, add tables ratios

\subsubsection{Height-Based Z-scores}
The Height-Based Z-scores (HBZs) are the Weight-for-Height Z-score (WHZ)
and Body Mass Index Z-score (BMIZ).
Where the BMI (or Quetelet) is a transformed version of the WHZ, which has a quadratic height effect.
The equation for BMI is:
\[
\textbf{BMI} = \frac{\textbf{weight(kg)}}{\textbf{height(m)}^2}
\]

@@

As \autoref{sa:hazwaz} shows both the Height-for-Age and the Weight-for-Age estmations for all three Right-Hand Side variations give similar results.
For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
In all cases the estimate has a p-value of less that \textbf{0.01}.
Meaning that (meta-discussion aside) the probabiliy that this coefficient represents a non-existant relation (Type II error) is less than one percent.
In the model 2 specification of the Weight-for-Height dependent variable, the p-value is even less that 0.001.
However, upon the inclusion of the interaction term (model 3) this falls back to below 0.01.

@@

\section{Conclusions and Limitations}
We find two results from out estimations.
Firstly, we find that there is a significant and consistant negative effect of the policy variable \textbf{elig.men.60} on the age-based z-scores
(i.e. Height for Age and Weight for Height).
Secondly, we find a consistent and negative effect of the men's pension variable (\textbf{w\_spen\_m}) on the Body-Mass-Index Z-scores.
Both of these effect are consistent across the different specifications used in our estimations.

>>>>

\subsubsection{Height-Based Z-scores}
\label{sa:se:hbz}
The Height-Based Z-scores (HBZs) are the Weight-for-Height Z-score (WHZ)
and Body Mass Index Z-score (BMIZ).
Where the BMI (or Quetelet) is a transformed version of the WHZ, which has a quadratic height effect.
The equation for BMI is:
\[
\textbf{BMI} = \frac{\textbf{weight(kg)}}{\textbf{height(m)}^2}
\]

@@

As \autoref{sa:hazwaz} shows both the Height-for-Age and the Weight-for-Age estimations for all three Right-Hand Side variations give similar results.
For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
In all cases the estimate has a p-value of less that \textbf{0.01}.
Meaning that (meta-discussion aside) the probabiliy that this coefficient represents a non-existant relation (Type II error) is less than one percent.
In the model 2 specification of the Weight-for-Height dependent variable, the p-value is even less that 0.001.
However, upon the inclusion of the interaction term (model 3) this falls back to below 0.01.

@@

We thus find a negative effect of the treatment on growth metrics.
Furthermore, for one height-based z-score we also find a negative effect of male pension recipients on growth metrics.
Additionaly, it is suprising that we find significant coefficients for \textbf{w\_spen\_m} in one height-based z-score (\textbf{BMIZ}), but not in the other \textbf{WHZ}.

The last results is especially surprising,
considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
and roughtly half of the estimates of the \textbf{BMIZ} estimations.

For the lower coefficient estimates, it is important to note that \textbf{BMIZ} is essentially a convex mapping of \textbf{WHZ},
since height is squared in the denominator of the BMI function, as described in \autoref{sa:se:hbz}.
In other words, the fact that the estimators, which give transformed coefficient estimates can have different significance levels,
can be explained as follows.
The squaring of the height in the denominator of the Body-Mass Index function, makes it a non-linear mapping of the Weight-for-Height Z-scores.
Furthermore, from the significance of the coefficients in the \textbf{BMIZ} estimations,
we can conclude that the coefficient estimates are higher that the standard error estimates,
by a factor of several times (for Degrees of Freedom $\sim 380$).
Combining the small estimates of the standard errors, with the convex mapping,
gives the results that the standard errors are scaled up to a lesser degree than the coefficient estimates.
This then gives the results, that with t-testing the significance of the convexly mapped coefficients and standard errors,
we can find significance at the 5\% level for the convexly mapped \textbf{BMIZ} estimates of \textbf{w\_spen\_m},
where for the \textbf{WHZ} estimates of \textbf{w\_spen\_m} we could not.

% DROP IN FEMALE RECIPIENTS, REMAIN LEVEL FOR MEN

\begin{table}[ht!]
\centering
\caption{Households with and without Male Pension Recipients}
\label{sa:ta:hmr}
    \begin{tabular}{l|rrrr}
    \hline
    Year              & 2008   & 2012   & 2013   & Overall \\
    \hline
    Male Recipient    & 612    & 595    & 623    & 1830    \\
    No Male Recipient & 6121   & 6138   & 6110   & 18369   \\
    Ratio of Male Recipients & 0.0909 & 0.0884 & 0.0925 & 0.0906  \\
    \end{tabular}
\end{table}

\begin{table}[ht!]
\centering
\caption{Households with and without Female Pension Recipients}
\label{sa:ta:fmr}
    \begin{tabular}{l|rrrr}
    \hline
    Year                & 2008   & 2012   & 2013   & Overall \\
    \hline
    Female Recipient    & 1637   & 1498   & 1509   & 4644    \\
    No Female Recipient & 5096   & 5235   & 5224   & 15555   \\
    Ratio               & 0.2431 & 0.2225 & 0.2241 & 0.2299  \\
    \end{tabular}
\end{table}

\section{Conclusions and Limitations}
We find two results from out estimations.
Firstly, we find that there is a significant and consistant negative effect of the policy variable \textbf{elig.men.60} on the age-based z-scores
(i.e.~Height for Age and Weight for Height).
Secondly, we find a consistent and negative effect of the men's pension variable (\textbf{w\_spen\_m}) on the Body-Mass-Index Z-scores.
Both of these effect are consistent across the different specifications used in our estimations.
